Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-29 ms.tex
model compare

\begin{deluxetable}{llllll}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:model_comparison}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 34.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 10.7 & 17.6 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 0.0 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 14.35 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 23.9 & 0.0 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}

@@

To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature). We found that the choice of model does not significantly change the results.  The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed). Since systematic noise is not strongly correlated with the thermal phase variation, the systematics-divided data are nearly identical for all the models.  This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve. In most phase bins, the planet-to-star flux agrees well within one sigma for all the models.

@@

All of the models provide reasonable fits to the data, but they yield signficantly different temperature maps. Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits. Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.

Spherical harmonics generally provide the best fit according to the AIC and BIC.

While the spherical harmonics model generally produces the best fits according to both the BIC and the AIC,

The kinematic model overpredicts the nightside flux. Model is not very flexible because nightside flux is assumed to be constant.
The two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

What is the difference in min/max temperature?

\subsection{Hotspot Offset}

\section{Retrieval}

>>>>

\begin{deluxetable}{llllll}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

@@

To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature). We found that the choice of model does not significantly change the results.  The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed). Since systematic noise is not strongly correlated with the thermal phase variation, the systematics-divided data are nearly identical for all the models.  This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve. In most phase bins, the planet-to-star flux agrees to well within one sigma for all the models.

@@

All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

%Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.

The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection. The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}. The sinusoid has eight free parameters (amplitude, phase offset, eclipse duration, ingress/egress duration, and midpoint and depth for each of two eclipses), whereas the spherical harmonics model has four (for degree two).  The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).  As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside. 
%The spherical harmonics model is strongly favored for most of the data sets according to the AIC and BIC. It has slightly more free parameters than the other models (four, versus three for the kinematic model and two for the two-temperature model).

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$. %For the WFC3 data, the peak temperature ranges from $2890$ to $3960$ K, and the minimum ranges from $0$ to $1980$ K.

These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCM (FIXME define?) simulations.

The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).

%The spherical harmonics model fits better according to the BIC and the AIC; however, it yields higher temperatures at the poles than at the equator, which does not agree with predictions from GCM simulations \citep{FIXME}.

\subsection{Hotspot Offset}
The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale). The faster the reradiation, the less heat can be redistributed to the nightside. We compared the measured hotspot offset for the different models and found FIXME.

\section{Retrieval}
We performed an atmospheric retrieval to determine the composition and thermal structure of the atmosphere of WASP-103b. We used the CHIMERA retrieval suite \citep{FIXME}, as well as. Briefly, the CHIMERA model fits for the atmospheric metallicity and carbon-to-oxygen ratio, assuming the atmosphere is in thermochemical equilibrium. The temperature-pressure profile is FIXME. We included opacity from the dominant absorbing species expected at the temperatures and pressures on WASP-103b, including FIXME. Previous analyses of emission spectra of the hottest planets have not included Hminus opacity, but we find that it has a significant effect on our results.

We also performed a simple grid search where we varied X.

\subsection{Thermal Inversion}
